### 2017-09-20 R3/R3-WP4/R3_ESD_NVE.Rmd
Updated Rmd script

Worshop on ESD 4 NVE 
-----------------------------------
title: "esd4nve_examples"
author: "Abdelkader Mezghani"
date: "March 11, 2016"
output: html_document
---

@@

## **Data & Structure**

```{r "setup", include=FALSE}
require("knitr")
opts_knit$set(root.dir = "~/DATA/data_esd_2016/fwddataforr3workshopenom2uker")
```

## Require the following libraries
```{r required R packages,echo=FALSE}
require(esd)
require(leaflet)
require(sp)
require(rgdal)
```

## R3 ESD & NVE
### Function for reading discharge data into the esd format

@@

#### Read meta data from the shape file

@@

#### Q Data Analysis
```{r data Analysis, warning=FALSE,eval=TRUE, eval=TRUE, warning=FALSE}
setwd('~/DATA/data_esd_2016/fwddataforr3workshopenom2uker/R3_WP4_Qdata_sep2017/')
load('q.nve.rda')
library(leaflet)

@@

## Downscaling monthly totals single discharge data @ Atnasjø

```{r,warning=FALSE,eval= FALSE}
library(esd)
load('~/DATA/data_esd_2016/fwddataforr3workshopenom2uker/R3_WP4_Qdata_sep2017/q.nve.rda')
selQ <- subset(q.nve,is = 1)
```

## Search the nearest meteorological station 
```{r}
# select nearest preciptiation stations
path.data <- '~/DATA/data_esd_2016/fwddataforr3workshopenom2uker/R3_WP4_Qdata_sep2017'

@@

### Select nearest temperature station
```{r selNearT}
path.data <- '~/DATA/data_esd_2016/fwddataforr3workshopenom2uker/R3_WP4_Qdata_sep2017'

@@

### Produce map with all layers
```{r selNearP}
labq <- paste(sep = "<br/>", paste("<b><a>",loc(q.nve),"</a></b>"))
labP <- paste(sep = "<br/>", paste("<b><a>", ssP$location,"</a></b>"))
labT <- paste(sep = "<br/>", paste("<b><a>", ssT$location,"</a></b>"))

@@

```{r}
load('~/DATA/data_esd_2016/fwddataforr3workshopenom2uker/R3_WP4_Qdata_sep2017/q.nve.rda')
q1 <- subset(q.nve,is = 1)
Pmm <- subset(as.4seasons(precip.ERAINT(lon = c(0,30), lat = c(50,85))),it = 'djf') 
# use already defined predictors or download from https://climexp.knmi.nl/selectfield_rea.cgi?id=someone@somewhere
uam <- subset(as.4seasons(q1),it = 'djf') # predictand
ds.uam <- DS(uam,EOF(Pmm))
plot(ds.uam)
```

```{r}
load('~/DATA/data_esd_2016/fwddataforr3workshopenom2uker/R3_WP4_Qdata_sep2017/q.nve.rda')
q1 <- subset(q.nve,is = 1)
Pmm <- subset(as.annual(subset(precip.ERAINT(lon = c(0,30), lat = c(50,85)),it = 'djf'),nmin=0),it = c(1979,2013)) 
# use already defined predictors or download from https://climexp.knmi.nl/selectfield_rea.cgi?id=someone@somewhere
uam <- subset(as.annual(subset(q1,it = 'djf'),nmin=0),it=c(1979,2013)) # predictand
ds.uam <- DS(uam,EOF(Pmm))
plot(ds.uam)
```

```{r}
load('~/DATA/data_esd_2016/fwddataforr3workshopenom2uker/R3_WP4_Qdata_sep2017/q.nve.rda')
q1 <- subset(q.nve,is = 1)
Pmm <- subset(as.annual(subset(t2m.ERAINT(lon = c(0,30), lat = c(50,85)),it = 'djf'),nmin=0),it = c(1979,2013)) 
# use already defined predictors or download from https://climexp.knmi.nl/selectfield_rea.cgi?id=someone@somewhere
uam <- subset(as.annual(subset(q1,it = 'djf'),nmin=0),it=c(1979,2013)) # predictand
ds.uam <- DS(uam,EOF(Pmm))
plot(ds.uam)
```

```{r monthly flow prediction, eval = TRUE}
# find and extract common dates

@@

```{r}
PRE <- precip.ERAINT(lon = c(0,30),lat =c(50,80))
Q <- subset(q.nve,is = 1)

ds.Q <- DS(subset(annual(Q),it = c(1950,2015)), EOF(subset(annual(PRE),it=c(1950,2015))))
plot(ds.Q)
```
```{r}
cor(subset(annual(Q),it=c(1960,2010)), subset(annual(subset(PRE,is=1)),it = c(1960,2010)),use = 'complete.obs')
```

>>>>

R3 Workpackage 4 on Extension to hydrological simulations
-----------------------------------
title: "R3_WP4_Hydrological"
author: "Abdelkader Mezghani"
date: "March 11, 2016"
output: html_document
---

@@

## Data Reading & Structure

```{r "setup"}
require("knitr")
opts_knit$set(root.dir = "~/git/esd_Rmarkdown/R3/R3-WP4/")
opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',echo=TRUE, warning=FALSE, message=FALSE) 
```

### Require the following libraries
```{r required R packages,echo=FALSE}
require(esd)
require(leaflet)
require(sp)
require(rgdal)
```

### Function for reading discharge data into the esd format

@@

### Read meta data from the shape file

@@

## Discharge Data Analysis
```{r data Analysis, warning=FALSE,eval=TRUE, eval=TRUE, warning=FALSE}
setwd('R3_WP4_Qdata_sep2017')
load('q.nve.rda')
library(leaflet)

@@

### Downscaling monthly totals @ a single discharge station

```{r,warning=FALSE,eval= FALSE}
library(esd)
load('R3_WP4_Qdata_sep2017/q.nve.rda')
selQ <- subset(q.nve,is = 1)
```

## Search the nearest meteorological station 
```{r,eval = FALSE}
# select nearest preciptiation stations
path.data <- 'R3_WP4_Qdata_sep2017'

@@

### Select nearest temperature station
```{r selNearT,eval = FALSE}
path.data <- 'R3_WP4_Qdata_sep2017'

@@

### Produce map with all layers
```{r selNearP, eval = TRUE}
labq <- paste(sep = "<br/>", paste("<b><a>",loc(q.nve),"</a></b>"))
labP <- paste(sep = "<br/>", paste("<b><a>", ssP$location,"</a></b>"))
labT <- paste(sep = "<br/>", paste("<b><a>", ssT$location,"</a></b>"))

@@

### Downscaling Examples
#### Example of Downscaling Seasonal values 
```{r}
load('R3_WP4_Qdata_sep2017/q.nve.rda')
q1 <- subset(q.nve,is = 1)
Pmm <- subset(as.4seasons(precip.ERAINT(lon = c(0,30), lat = c(50,85))),it = 'djf') 
# use already defined predictors or download from https://climexp.knmi.nl/selectfield_rea.cgi?id=someone@somewhere
uam <- subset(as.4seasons(q1),it = 'djf') # predictand
ds.uam <- DS(uam,EOF(Pmm))
plot(ds.uam)
```

#### Example of downscaling annual means using ERAINT precip as predictor
```{r}
load('R3_WP4_Qdata_sep2017/q.nve.rda')
q1 <- subset(q.nve,is = 1)
Pmm <- subset(as.annual(subset(precip.ERAINT(lon = c(0,30), lat = c(50,85)),it = 'djf'),nmin=0),it = c(1979,2013)) 
# use already defined predictors or download from https://climexp.knmi.nl/selectfield_rea.cgi?id=someone@somewhere
uam <- subset(as.annual(subset(q1,it = 'djf'),nmin=0),it=c(1979,2013)) # predictand
ds.uam <- DS(uam,EOF(Pmm))
plot(ds.uam)
```

#### Example of downscaling annual means using ERAINT T2m as predictor
```{r,eval = FALSE}
load('R3_WP4_Qdata_sep2017/q.nve.rda')
q1 <- subset(q.nve,is = 1)
Pmm <- subset(as.annual(subset(t2m.ERAINT(lon = c(0,30), lat = c(50,85)),it = 'djf'),nmin=0),it = c(1979,2013)) 
# use already defined predictors or download from https://climexp.knmi.nl/selectfield_rea.cgi?id=someone@somewhere
uam <- subset(as.annual(subset(q1,it = 'djf'),nmin=0),it=c(1979,2013)) # predictand
ds.uam <- DS(uam,EOF(Pmm))
plot(ds.uam)
```

### Downscaling of monthly discharge values # OLD example not run
```{r monthly flow prediction, eval = FALSE}
# This is an old example, not working for now !!!

@@
